Data Preparation

### 2019-01-10 Data Preparation.Rmd
more suitable names to var. of d_transcript

###Renaming Variables
First we rename the variable names to make them more comprehensible:
```{r}
d_rename <-d_dirt %>%
  rename(
    ID                     =  "X...Student.Number", 
    Code                   =  "Module..Abbrev..", 
    `Course Title`         =  "Module..Desc..",
    `Program Abbreviation` =  "Program..Abbreviation.", 
    `Program Description`  =  "Program..Description.",               
    Year                   =  "Academic.Year",                      
    Session                =  "Academic.Session",
    `Appraisal Code`       =  "Appraisal.Type",                     
    `Appraisal Title`      =  "Appraisal..Description.",             
    Attempt                =  "Number.rep..attemp",                 
    Grade                  =  "Grade.symbol",                        
    `Appraisal Status`     =  "Appraisal.Status",                   
    `Appraisal Status Description` =  "Appraisal.Status..Desc..",    #is only NA: unique(d4$Appraisal.Status..Desc..)       
    `Booking Reason`       =  "Module.Booking.Reason..Description.",
    `Appraisal Date`       =  "Appraisal.date",                      
    `Attempted Credits`    =  "Attempted.credits",                  
    `Earned Credit`        =  "Earned.Credits",                      
    `Credit Type`          =  "Credit.Type",                        
    `Personnel Number`     =  "Personnel.Number",                  
    `Name (Employee/Applicant)`=  "Name.of.employee.or.applicant",      
    `Individual Work`      =  "Individual.Work",                     
    `Academic Work ID`     =  "Academic.Work.ID",                   
    `Booking Status`       =  "Booking.Status",                      #empty
    `Booking Status Description` =  "Booking.Status..Desc..",             
    `Event Object Id`      =  "Event.Object.Id",                     #empty forwards and including      
    `Business Event Abbreviation` =  "Business.event.abbr.",               
    `Event Description`    =  "Event.Description",                   
    `Start time`           =  "Start.time",                         
    `End time`             =  "End.time",                            
    `Date`                 =  "Date",                               
    `Studyplan`            =  "Studyplan",                           
    `Conditional booking`  =  "Conditiona.booking",                 
    `Wachtlist`            =  "Wachtlist",                           
    `Object ID`            =  "Object.ID",                          
    `Object Name`          =  "Object.name",                         
    `Start Date`           =  "Start.date",                         
    `End Date`             =  "End.Date",                            
    `Number of Weeks`      =  "Number.of.weeks",                      #until this one next has values              
    `Appraiser ID`         =  "Appraiser.ID",                        
    `Appraiser Name`       =  "Appraiser.Name"

  ) 
```

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage.

NOTE TO RAPHAEL: This was in case we later wanted to use any of the non-empty variables, but I don't think we need this anymore, so you can safely just cut this section and select fewer variables later. 
```{r}
not_keep <- c("Booking Status",
              "Appraisal Status Description",
              "Credit Type",
              "Personnel Number",
              "Event Object Id",     
              "Business Event Abbreviation",               
              "Event Description",                   
              "Start time",                         
              "End time",                            
              "Date",                               
              "Studyplan",                           
              "Conditional booking",                 
              "Wachtlist",                           
              "Object ID", #? has values e.g. 50236380                        
              "Object Name",  #?  has values, e.g. "BE-Universitair Ziekenhuis Brussel"
              "Start Date",   #? has values, e.g.  "12/16/13"                     
              "End Date",     #? has values, e.g. "5/14/10"                      
              "Number of Weeks", 
              "Name (Employee/Applicant)",
              "Appraiser ID",      #HAS VALUES BUT NOT IMPORTANT, e.g. 70011933
              "Appraiser Name",    #HAS VALUES BUT NOT IMPORTANT, e.g.  J.J. Briede  
              "Academic Work ID",  #has values, eg.53EA405080711826E10000008978030A
              "Attempted Credits", #HAS VALUES BUT NOT IMPORTANT
              "Earned Credit",
              "Individual Work",
              "Appraisal Status",
              "Booking Reason",
              "Appraisal Date" #day when grades were put in
              ) 
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
```{r}
d_rename <-d_rename %>%
  mutate(Period= case_when(
    (Session==100)~"1",
    (Session==101)~"1",
    (Session==102)~"1",
    #(Session==190)~"1", #is not there
    (Session==191)~"1",
    (Session==200)~"2",
    (Session==201)~"2",
    (Session==202)~"2",
    (Session==291)~"2",
    (Session==300)~"3",
    (Session==330)~"3",
    (Session==350)~"3",
    (Session==400)~"4",
    (Session==410)~"4",
    (Session==420)~"4",
    (Session==430)~"4",
    (Session==450)~"4",
    (Session==460)~"4",
    (Session==481)~"4",
    (Session==482)~"4",
    (Session==500)~"5",
    (Session==520)~"5",
    (Session==530)~"5",
    (Session==550)~"5",
    (Session==551)~"5",
    (Session==560)~"5",
    (Session==552)~"5",
    (Session==580)~"5",
    (Session==600)~"6",
    (Session==610)~"6",
    (Session==620)~"6",
    (Session==630)~"6",
    (Session==650)~"6",
    (Session==660)~"6",
    (Session==680)~"5",#WHHHHHHHHHHHHHHHHHAAAAAAAAAAATTTTTTTTTTT?????? Why is this period 5
    (Session==1)~"1,2,3,4,5,6",
    (Session==2)~"1,2,3",
    (Session==3)~"4,5,6",
    #(Session==203)~c("2","3"),#is not there
    (Session==350)~"3,4,5",
    (Session==403)~"4,5",
    (Session==900)~"1,2,3,4,5,6",
    (Session==910)~"1", #ASK ABOUT THE 900'S
    (Session==911)~"1",
    (Session==912)~"1",
    (Session==913)~"1",
    (Session==914)~"1",
    (Session==915)~"1",
    (Session==916)~"1",
    (Session==920)~"1",
    (Session==923)~"1",
    (Session==930)~"1",
    (Session==940)~"1",
    (Session==950)~"1",
    (Session==960)~"1"
     )
           )
```
###Dropping useless variables:
Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:

>>>>

###Renaming Variables
First we rename the variable names to make them more comprehensible:
```{r}

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
```{r}
d_transcript <- d_transcript %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Appraisal (Description)`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
```{r}
d_rename <- d_rename %>%
  mutate(Period= case_when(
    (Session==100)~"1",
    (Session==101)~"1",
    (Session==102)~"1",
    #(Session==190)~"1", #is not there
    (Session==191)~"1",
    (Session==200)~"2",
    (Session==201)~"2",
    (Session==202)~"2",
    (Session==291)~"2",
    (Session==300)~"3",
    (Session==330)~"3",
    (Session==350)~"3",
    (Session==400)~"4",
    (Session==410)~"4",
    (Session==420)~"4",
    (Session==430)~"4",
    (Session==450)~"4",
    (Session==460)~"4",
    (Session==481)~"4",
    (Session==482)~"4",
    (Session==500)~"5",
    (Session==520)~"5",
    (Session==530)~"5",
    (Session==550)~"5",
    (Session==551)~"5",
    (Session==560)~"5",
    (Session==552)~"5",
    (Session==580)~"5",
    (Session==600)~"6",
    (Session==610)~"6",
    (Session==620)~"6",
    (Session==630)~"6",
    (Session==650)~"6",
    (Session==660)~"6",
    (Session==680)~"5",#WHHHHHHHHHHHHHHHHHAAAAAAAAAAATTTTTTTTTTT?????? Why is this period 5
    (Session==1)~"1,2,3,4,5,6",
    (Session==2)~"1,2,3",
    (Session==3)~"4,5,6",
    #(Session==203)~c("2","3"),#is not there
    (Session==350)~"3,4,5",
    (Session==403)~"4,5",
    (Session==900)~"1,2,3,4,5,6",
    (Session==910)~"1", #ASK ABOUT THE 900'S
    (Session==911)~"1",
    (Session==912)~"1",
    (Session==913)~"1",
    (Session==914)~"1",
    (Session==915)~"1",
    (Session==916)~"1",
    (Session==920)~"1",
    (Session==923)~"1",
    (Session==930)~"1",
    (Session==940)~"1",
    (Session==950)~"1",
    (Session==960)~"1"
     )
           )
```
###Dropping useless variables:
Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:
